How not to constructivize cohomology

### 2018-10-15 slides-pssl104.tex
typo

  \jnote{4-}{Even though constructively we can't show that any inhabited set is
  flabby, we can still verify that there are \emph{enough flabby sets}.}

  \jnote{5-}{A module is \emph{flabby} if and only if its underlying set is.
  We'll see what the significance of this open question is later on.}
\end{frame}

>>>>

  \jnote{4-}{Even though constructively we can't show that any inhabited set is
  flabby, we can still verify that there are \emph{enough flabby sets}.}
  \jnote{5-}{However it's unknown whether there are \emph{enough flabby
  modules}. (A module is \emph{flabby} if and only if its underlying set is.)
  We'll see what the significance of this open question is later on.}
\end{frame}
